Coupling PDEs on XD-YD domains with Lagrange multipliers

### 2019-05-09 stab/stab.tex

In the following experiments $\Omega=(0, 1)^2$, $\Gamma_L=\left\{(x, y)\in\partial\Omega; x=0\right\}$
while $\Gamma_D=\partial\Omega\setminus \Gamma_L$. Letting $\Omega_h$, $\Gamma_H$
denote respectively the discretizations of $\Omega$ and $\Gamma_L$ we shall consider
two different geometrical settings, cf. Figure \ref{fig:domains}, (i) either
$\Gamma_H$ is the trace mesh (on $\Gamma_L$) of $\Omega$, i.e. there is a one-to-one
mapping between vertices/cells of the two meshes or (ii) $\Gamma_H$ is not the
trace mesh of $\Omega$ and $\Gamma_H$ is finer relative to the trace mesh.
We shall subsequently refer to the two cases as \emph{matching} and \emph{non-matching}.

%
\begin{figure}[h]
  \begin{center}
\begin{tikzpicture}
  \draw[black, very thick] (1,0) rectangle (4, 3);
  \draw[black, very thick] (1,0) -- (4, 3);
  \node[fill=white, opacity=0.9] at (2.5, 1.5) {$\Omega_{h}$};

@@

  \draw[black, very thick] (0.5,0) -- (0.5, 3);
  \node[opacity=0.9, left] at (0.5, 1.5) {$\Gamma_{H}$};

  \node[mark size=3pt, color=black] at (0.5, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (0.5, 3) {\pgfuseplotmark{*}};
\end{tikzpicture}
%
\hspace{50pt}
%
\begin{tikzpicture}
  \draw[black, very thick] (1,0) rectangle (4, 3);
  \draw[black, very thick] (1,0) -- (4, 3);
  \node[fill=white, opacity=0.9] at (2.5, 1.5) {$\Omega_{h}$};

@@

  \draw[black, very thick] (0.5,0) -- (0.5, 3);
  \node[opacity=0.9, left] at (0.5, 1.5) {$\Gamma_{H}$};

@@

\subsubsection{Non-matching case} Here $\dim Q_H$ is (considerably) larger
than the trace space of $V_h$ and stabilization of \cite{burman2009interior}
is needed to obtain inf-sup stability. More precisely, the discretization
of \eqref{eq:bab} reads: Find $u\in V_h$, $q\in Q_H$ such that
%
\begin{equation}\label{eq:p1_stab}
\begin{aligned}
&\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v &\forall v\in V_h,\\
  &\int_{\Gamma_L}q u  &-\gamma \sum_{K\in\Gamma_H}\int_{K} H_K^3\nabla p\cdot\nabla q &= \int_{\Gamma} g q &\forall q\in Q_H.
  \end{aligned}
\end{equation}
%
Here $\gamma$ is a stabilization parameter and we use $\gamma=1$ in the
following. As before, the trial and test functions of the space $Q_H$ are
constructed such that they satisfy the boundary conditions $p=0$ on $\partial\Gamma_L$.

MinRes iteration counts with the Riesz map preconditioner are shown in
Table \ref{tab:p1_p1}. Here, the $Q$ block of the preconditioner is based
on the inverse of the bilinear form
\[
\langle -\Delta_{00}^{1/2} p, q\rangle + \sum_{K\in\Gamma_H}\int_{K} H_K^3\nabla p \cdot\nabla q,\quad p, q\in Q_H.
\]
%

\begin{table}
  \begin{center}
    \footnotesize{
  \begin{tabular}{c|cc|c|c||cc|c|c}
    \hline
    $h$ & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
        & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
    \hline
8.84E-02 & 6.91E+00(--)   & 6.37E+00(--)   & 29 & 5.131 & 6.90E+00(--)  & 5.94E+00(--)    & 31 & 4.836\\
4.42E-02 & 3.54E+00(0.97) & 1.61E+00(1.98) & 26 & 5.176 & 3.54E+00(0.96) & 1.76E+00(1.75) & 29 & 4.846\\
2.21E-02 & 1.78E+00(0.99) & 5.45E-01(1.56) & 26 & 5.191 & 1.78E+00(0.99) & 5.95E-01(1.57) & 28 & 4.851\\
1.10E-02 & 8.93E-01(1.00) & 3.11E-01(0.81) & 25 & 5.195 & 8.93E-01(1.00) & 3.24E-01(0.88) & 26 & 4.853\\
5.52E-03 & 4.46E-01(1.00) & 2.12E-01(0.55) & 24 & 5.196 & 4.46E-01(1.00) & 2.16E-01(0.59) & 26 & 4.853\\
2.76E-03 & 2.23E-01(1.00) & 1.49E-01(0.51) & 24 & 5.196 & 2.23E-01(1.00) & 1.50E-01(0.52) & 24 & 4.854\\
1.38E-03 & 1.12E-01(1.00) & 1.06E-01(0.50) & 22 & --    & 1.12E-01(1.00) & 1.06E-01(0.51) & 22 & --   \\
    \hline
  \end{tabular}
  }
    \caption{Approximation errors, number of preconditioned MinRes iterations ($n$) and
      condition number of the preconditioned problem \eqref{eq:bab} ($\kappa$) discretized
      with P1-P1 elements. (left) Matching case. (right) Non-matching case.}
  \label{tab:p1_p1}
  \end{center}
\end{table}
%
Concerning approximation properties of the discretization, note that the error
for the multiplier is reported in the $L^2$ norm and not the natural $H^{-1/2}$
norm. Nevertheless, the rate seems sub-optimal. This is likely due to the fact
that the multiplier in the manufactured test case does not satisfy the
Dirichlet boundary conditions employed in the discrete problem.

\subsection{Discretization by P1-P0 elements}\label{sec:p1_p0}
We consider finite element discretization of \eqref{eq:bab} in terms P1 elements
for the space $V$ while the multiplier space uses piecewise constants elements
(P0). In both the matching and non-matching case the discretization is unstable
and inf-sup stability is obtained by using stabilization \cite{burman2014projection}.
That is, the disretization of \eqref{eq:bab} reads: Find $u\in V_h$, $q\in Q_H$ such that
%
\begin{equation}\label{eq:p0_stab}
\begin{aligned}
&\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v &\forall v\in V_h,\\
  &\int_{\Gamma_L}q u  &-\gamma \sum_{\mathcal{V}^0} \avg{H_K}^2\jump{p}\jump{q} &= \int_{\Gamma} g q &\forall q\in Q_H,
  \end{aligned}
\end{equation}
%
where $\mathcal{V}^0$ is the set of all interior vertices of $\Gamma_H$.

@@

\begin{table}
  \begin{center}
    \footnotesize{
  \begin{tabular}{c|cc|c|c||cc|c|c}
    \hline
    $h$ & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
        & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
    \hline
8.84E-02 & 6.88E+00(--)   & 2.83E+00(--)  & 26 & 4.749  & 6.91E+00(--)   & 1.17E+01(--)  & 35 & 6.940 \\
4.42E-02 & 3.54E+00(0.96) & 2.12E+00(0.42)& 28 & 4.817  & 3.54E+00(0.96) & 2.33E+00(2.33)& 35 & 6.973 \\
2.21E-02 & 1.78E+00(0.99) & 7.42E-01(1.51)& 28 & 4.840  & 1.78E+00(0.99) & 4.91E-01(2.24)& 30 & 6.987 \\
1.10E-02 & 8.93E-01(1.00) & 2.17E-01(1.78)& 25 & 4.850  & 8.93E-01(1.00) & 1.46E-01(1.75)& 28 & 6.994 \\
5.52E-03 & 4.46E-01(1.00) & 8.90E-02(1.28)& 23 & 4.853  & 4.46E-01(1.00) & 5.90E-02(1.31)& 27 & 6.996 \\
2.76E-03 & 2.23E-01(1.00) & 4.28E-02(1.06)& 23 & 4.853  & 2.23E-01(1.00) & 2.77E-02(1.09)& 26 & 6.995 \\
1.38E-03 & 1.12E-01(1.00) & 2.12E-02(1.01)& 23 & --     & 1.12E-01(1.00) & 1.36E-02(1.02)& 25 & --    \\  
    \hline
  \end{tabular}
    }
    \caption{Approximation errors, number of preconditioned MinRes iterations ($n$) and
      condition number of the preconditioned problem \eqref{eq:bab} ($\kappa$) discretized
      with P1-P0 elements. (left) Matching case. (right) Non-matching case.}
  \label{tab:p1_p0}
  \end{center}
\end{table}

@@

  \node[black!60!white, fill=white, opacity=0.9] at (1, 2) {$\Omega^{-}$};
  \node[black!60!white, fill=white, opacity=0.9] at (3, 2) {$\Omega^{+}$};
  \node[black!60!white, fill=white, opacity=0.9, right] at (4, 0) {$\Gamma_D$};

  \draw[black, very thick] (2, 0) -- (2, 4);
  \draw[->, black] (2, 1) -- (3, 1);
  \node[fill=white, opacity=0.9, above] at (2.5, 1) {$n$};
  \node[fill=white, opacity=0.9, right] at (2.025, 2) {$\Gamma$};
\end{tikzpicture}
    \end{center}
    %\vspace{-20pt}
    \caption{Schematic domain of coupled multiscale problem.}
    \label{fig:coupled_domain}
    %\vspace{5pt}    
\end{figure}
\end{minipage}
%
Let $\Omega=\Omega^{+}\cup\Omega^{-}$ and $\Gamma_D=\Gamma^{+}_D\cup\Gamma^{-}_N$.
Introducing a Lagrange multiplier $p=\jump{\nabla\cdot n}\in Q=(H^{-1/2}_{00}(\Gamma))^{\prime}$
the weak form of \eqref{eq:coupled} reads: Find $u\in V=H^1_{0, \Gamma_D}(\Omega)$,
$\hat{v}\in\hat{V}=H^1_{0, \partial\Gamma}(\Gamma)$, $p\in Q$ such that
%
\begin{equation}\label{eq:coupled_weak}
  \begin{aligned}
    &\int_{\Omega}\nabla u\cdot \nabla v &\phantom{+\int_{\Gamma}\nabla \hat{u}\cdot \nabla \hat{v}} &+\int{\Gamma}p v &= \int_{\Omega}f v \quad &\forall v\in V,\\
    &\phantom{\int_{\Omega}\nabla u\cdot \nabla v} &+{\int_{\Gamma}\nabla \hat{u}\cdot \nabla \hat{v}} &-\int{\Gamma}p\hat{v} &= \int_{\Gamma}\hat{f}\hat{v} \quad &\forall \hat{v}\in \hat{V},\\
    &\int_{\Gamma}u q &-\int_{\Gamma}\hat{u}q &\phantom{-\int{\Gamma}q\hat{v}} &= \int_{\Gamma}h q \quad &\forall q\in Q.
  \end{aligned}
\end{equation}
%
\begin{figure}[h]
  \begin{center}
    \begin{tikzpicture}[scale=0.60]
      % Minus
  \draw[black, very thick] (1,0) rectangle (4, 3);
  \draw[black, very thick] (1,0) -- (4, 3);
  \node[fill=white, opacity=0.9] at (2.5, 1.5) {$\Omega^{-}_{h}$};

@@

  \draw[black, very thick] (4.5,0) -- (4.5, 3);
  \node[opacity=0.9, below] at (4.5, 0) {$\Gamma_{H}$};

  \node[mark size=3pt, color=black] at (4.5, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (4.5, 3) {\pgfuseplotmark{*}};
  % Right
    \draw[black, very thick] (5,0) rectangle (8, 3);
  \draw[black, very thick] (5,0) -- (8, 3);
  \node[fill=white, opacity=0.9] at (6.5, 1.5) {$\Omega^{+}_{h}$};

  \node[mark size=3pt, color=black] at (5, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (8, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (5, 3) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (8, 3) {\pgfuseplotmark{*}};
\end{tikzpicture}
    %
    \hspace{10pt}
    \begin{tikzpicture}[scale=0.60]
      % Minus
  \draw[black, very thick] (1,0) rectangle (4, 3);
  \draw[black, very thick] (1,0) -- (4, 3);
  \node[fill=white, opacity=0.9] at (2.75, 1.5) {$\Omega^{-}_{h}$};

@@

  \draw[black, thin, dotted] (4, 0) -- (4.5, 0);
  \draw[black, thin, dotted] (4, 3) -- (4.5, 3);
  % Center
  \draw[black, thin, dotted] (4.5, 0) -- (5, 0);
  \draw[black, thin, dotted] (4.5, 3) -- (5, 3);
     % Center
  \draw[black, very thick] (4.5,0) -- (4.5, 3);
  \node[opacity=0.9, below] at (4.5, 0) {$\Gamma_{H}$};

  \node[mark size=3pt, color=black] at (4.5, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (4.5, 1) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (4.5, 2) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (4.5, 3) {\pgfuseplotmark{*}};
  % Right
    \draw[black, very thick] (5,0) rectangle (8, 3);
  \draw[black, very thick] (5,0) -- (8, 3);
  \node[fill=white, opacity=0.9] at (6.5, 1.5) {$\Omega^{+}_{h}$};

  \node[mark size=3pt, color=black] at (5, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (8, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (5, 3) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (8, 3) {\pgfuseplotmark{*}};
    \end{tikzpicture}
        %
    \hspace{10pt}
    \begin{tikzpicture}[scale=0.60]
      % Minus
  \draw[black, very thick] (0,0) rectangle (3, 3);
  \draw[black, very thick] (0,0) -- (3, 3);
  \node[fill=white, opacity=0.9] at (2.25, 1.5) {$\Omega^{-}_{h}$};

@@

     % Center
  \draw[black, very thick] (4.5,0) -- (4.5, 3);
  \node[opacity=0.9, below] at (4.5, 0) {$\Gamma_{H}$};

@@

  \draw[black, very thick] (3,0) -- (6, 0);
  \draw[black, very thick] (3,0) -- (6, 3);
  \draw[black, very thick] (3,3) -- (6, 3);  
  % Right
    \draw[black, very thick] (6,0) rectangle (9, 3);
  \draw[black, very thick] (6,0) -- (9, 3);
  \node[fill=white, opacity=0.9] at (6.75, 1.5) {$\Omega^{+}_{h}$};

  \node[mark size=3pt, color=black] at (6, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (9, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (6, 3) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (9, 3) {\pgfuseplotmark{*}};
\end{tikzpicture}
%
\end{center}
  \caption{Different mesh settings considered for the coupled problem
    \eqref{eq:coupled_weak}: conforming matching, conforming non-matching,
    non-conforming (from left to right).
  }
\label{fig:multi_domains}
\end{figure}
%
In the following $\Omega=(0, 1)$, $\Gamma=\left\{(x, y)\in\Omega; x=\tfrac{1}{2}\right\}$
and based on the properties of the finite element meshes $\Omega_h$, $\Gamma_H$
we shall distinguish three different settings, cf. Figure \ref{fig:multi_domains}.
Here, a conforming case implies that the trace mesh of $\Omega_h$ on $\Gamma$
consists only of the existing facets of the mesh. In the conforming setting 
we consider matching and non-matching cases as defined above. We remark
that the approximation of the space $\hat{V}$ shall always be constructed
on the multiplier mesh $\Gamma_H$.

\subsection{P1-P1-P1 discretization with $\Gamma$ conformity}
Let us first consider a conforming setting and an approximation of all
the spaces involved in \eqref{eq:coupled_weak} in terms of P1 elements.
As with the Babu{\v s}ka problem \eqref{eq:bab} the discrete multiplier
space is such that $q=0$ on $\partial\Gamma$ for all $q\in Q_H$. In fact,
the boundary conditions are necessary to obtain an invertible linear system.

>>>>

In the following experiments $\Omega=(0, 1)^2$, $\Gamma_L=\left\{(x, y)\in\partial\Omega; x=0\right\}$
while $\Gamma_D=\partial\Omega\setminus \Gamma_L$. Letting $\Omega_H$, $\Gamma_h$
denote respectively the discretizations of $\Omega$ and $\Gamma_L$ we shall consider
two different geometrical settings, cf. Figure \ref{fig:domains}, (i) either
$\Gamma_h$ is the trace mesh (on $\Gamma_L$) of $\Omega$, i.e. there is a one-to-one
mapping between vertices/cells of the two meshes or (ii) $\Gamma_h$ is not the
trace mesh of $\Omega$ and $\Gamma_h$ is finer relative to the trace mesh.
We shall subsequently refer to the two cases as \emph{matching} and \emph{non-matching}.

%
\begin{figure}[h]
  \begin{center}
\begin{tikzpicture}
  \draw[black, very thick] (1,0) rectangle (4, 3);
  \draw[black, very thick] (1,0) -- (4, 3);
  \node[fill=white, opacity=0.9] at (2.5, 1.5) {$\Omega_{H}$};

@@

  \draw[black, very thick] (0.5,0) -- (0.5, 3);
  \node[opacity=0.9, left] at (0.5, 1.5) {$\Gamma_{h}$};

  \node[mark size=3pt, color=black] at (0.5, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (0.5, 3) {\pgfuseplotmark{*}};
\end{tikzpicture}
%
\hspace{50pt}
%
\begin{tikzpicture}
  \draw[black, very thick] (1,0) rectangle (4, 3);
  \draw[black, very thick] (1,0) -- (4, 3);
  \node[fill=white, opacity=0.9] at (2.5, 1.5) {$\Omega_{H}$};

@@

  \draw[black, very thick] (0.5,0) -- (0.5, 3);
  \node[opacity=0.9, left] at (0.5, 1.5) {$\Gamma_{h}$};

@@

\subsubsection{Non-matching case} Here $\dim Q_h$ is (considerably) larger
than the trace space of $V_H$ and stabilization of \cite{burman2009interior}
is needed to obtain inf-sup stability. More precisely, the discretization
of \eqref{eq:bab} reads: Find $u\in V_H$, $q\in Q_h$ such that
%
\begin{equation}\label{eq:p1_stab}
\begin{aligned}
&\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v &\forall v\in V_H,\\
  &\int_{\Gamma_L}q u  &-\gamma \sum_{K\in\Gamma_h}\int_{K} h_K^3\nabla p\cdot\nabla q &= \int_{\Gamma} g q &\forall q\in Q_h.
  \end{aligned}
\end{equation}
%
Here $\gamma$ is a stabilization parameter and we use $\gamma=1$ in the
following. As before, the trial and test functions of the space $Q_h$ are
constructed such that they satisfy the boundary conditions $p=0$ on $\partial\Gamma_L$.

MinRes iteration counts with the Riesz map preconditioner are shown in
Table \ref{tab:p1_p1}. Here, the $Q$ block of the preconditioner is based
on the inverse of the bilinear form
\[
\langle -\Delta_{00}^{1/2} p, q\rangle + \sum_{K\in\Gamma_h}\int_{K} h_K^3\nabla p \cdot\nabla q,\quad p, q\in Q_h.
\]
%

\begin{table}
  \begin{center}
    \footnotesize{
  \begin{tabular}{c|cc|c|c||cc|c|c}
    \hline
    $h$ & $\norm{u-u_H}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
        & $\norm{u-u_H}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
    \hline
8.84E-02 & 6.91E+00(--)   & 6.37E+00(--)   & 29 & 5.131 & 6.90E+00(--)  & 5.94E+00(--)    & 31 & 4.836\\
4.42E-02 & 3.54E+00(0.97) & 1.61E+00(1.98) & 26 & 5.176 & 3.54E+00(0.96) & 1.76E+00(1.75) & 29 & 4.846\\
2.21E-02 & 1.78E+00(0.99) & 5.45E-01(1.56) & 26 & 5.191 & 1.78E+00(0.99) & 5.95E-01(1.57) & 28 & 4.851\\
1.10E-02 & 8.93E-01(1.00) & 3.11E-01(0.81) & 25 & 5.195 & 8.93E-01(1.00) & 3.24E-01(0.88) & 26 & 4.853\\
5.52E-03 & 4.46E-01(1.00) & 2.12E-01(0.55) & 24 & 5.196 & 4.46E-01(1.00) & 2.16E-01(0.59) & 26 & 4.853\\
2.76E-03 & 2.23E-01(1.00) & 1.49E-01(0.51) & 24 & 5.196 & 2.23E-01(1.00) & 1.50E-01(0.52) & 24 & 4.854\\
1.38E-03 & 1.12E-01(1.00) & 1.06E-01(0.50) & 22 & --    & 1.12E-01(1.00) & 1.06E-01(0.51) & 22 & --   \\
    \hline
  \end{tabular}
  }
    \caption{Approximation errors, number of preconditioned MinRes iterations ($n$) and
      condition number of the preconditioned problem \eqref{eq:bab} ($\kappa$) discretized
      with P1-P1 elements. (left) Matching case. (right) Non-matching case.}
  \label{tab:p1_p1}
  \end{center}
\end{table}
%
Concerning approximation properties of the discretization, note that the error
for the multiplier is reported in the $L^2$ norm and not the natural $H^{-1/2}$
norm. Nevertheless, the rate seems sub-optimal. This is likely due to the fact
that the multiplier in the manufactured test case does not satisfy the
Dirichlet boundary conditions employed in the discrete problem.

\subsection{Discretization by P1-P0 elements}\label{sec:p1_p0}
We consider finite element discretization of \eqref{eq:bab} in terms P1 elements
for the space $V$ while the multiplier space uses piecewise constants elements
(P0). In both the matching and non-matching case the discretization is unstable
and inf-sup stability is obtained by using stabilization \cite{burman2014projection}.
That is, the disretization of \eqref{eq:bab} reads: Find $u\in V_H$, $q\in Q_h$ such that
%
\begin{equation}\label{eq:p0_stab}
\begin{aligned}
&\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v &\forall v\in V_H,\\
  &\int_{\Gamma_L}q u  &-\gamma \sum_{\mathcal{V}^0} \avg{h_K}^2\jump{p}\jump{q} &= \int_{\Gamma} g q &\forall q\in Q_h,
  \end{aligned}
\end{equation}
%
where $\mathcal{V}^0$ is the set of all interior vertices of $\Gamma_h$.

@@

\begin{table}
  \begin{center}
    \footnotesize{
  \begin{tabular}{c|cc|c|c||cc|c|c}
    \hline
    $h$ & $\norm{u-u_H}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
        & $\norm{u-u_H}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
    \hline
8.84E-02 & 6.88E+00(--)   & 2.83E+00(--)  & 26 & 4.749  & 6.91E+00(--)   & 1.17E+01(--)  & 35 & 6.940 \\
4.42E-02 & 3.54E+00(0.96) & 2.12E+00(0.42)& 28 & 4.817  & 3.54E+00(0.96) & 2.33E+00(2.33)& 35 & 6.973 \\
2.21E-02 & 1.78E+00(0.99) & 7.42E-01(1.51)& 28 & 4.840  & 1.78E+00(0.99) & 4.91E-01(2.24)& 30 & 6.987 \\
1.10E-02 & 8.93E-01(1.00) & 2.17E-01(1.78)& 25 & 4.850  & 8.93E-01(1.00) & 1.46E-01(1.75)& 28 & 6.994 \\
5.52E-03 & 4.46E-01(1.00) & 8.90E-02(1.28)& 23 & 4.853  & 4.46E-01(1.00) & 5.90E-02(1.31)& 27 & 6.996 \\
2.76E-03 & 2.23E-01(1.00) & 4.28E-02(1.06)& 23 & 4.853  & 2.23E-01(1.00) & 2.77E-02(1.09)& 26 & 6.995 \\
1.38E-03 & 1.12E-01(1.00) & 2.12E-02(1.01)& 23 & --     & 1.12E-01(1.00) & 1.36E-02(1.02)& 25 & --    \\  
    \hline
  \end{tabular}
    }
    \caption{Approximation errors, number of preconditioned MinRes iterations ($n$) and
      condition number of the preconditioned problem \eqref{eq:bab} ($\kappa$) discretized
      with P1-P0 elements. (left) Matching case. (right) Non-matching case.}
  \label{tab:p1_p0}
  \end{center}
\end{table}

@@

  \node[black!60!white, fill=white, opacity=0.9] at (1, 2) {$\Omega^{-}$};
  \node[black!60!white, fill=white, opacity=0.9] at (3, 2) {$\Omega^{+}$};
  \node[black!60!white, opacity=0.9, right] at (4, 0) {$\Gamma_D$};

  \draw[black, very thick] (2, 0) -- (2, 4);
  \draw[->, black] (2, 1) -- (3, 1);
  \node[fill=white, opacity=0.9, above] at (2.5, 1) {$n$};
  \node[fill=white, opacity=0.9, right] at (2.025, 2) {$\Gamma$};
\end{tikzpicture}
    \end{center}
    %\vspace{-20pt}
    \caption{Schematic domain of coupled multiscale problem.}
    \label{fig:coupled_domain}
    %\vspace{5pt}    
\end{figure}
\end{minipage}
%
Let $\Omega=\Omega^{+}\cup\Omega^{-}$ and $\Gamma_D=\Gamma^{+}_D\cup\Gamma^{-}_N$.
Introducing a Lagrange multiplier $p=\jump{\nabla u \cdot n}\in Q=(H^{-1/2}_{00}(\Gamma))^{\prime}$
the weak form of \eqref{eq:coupled} reads: Find $u\in V=H^1_{0, \Gamma_D}(\Omega)$,
$\hat{v}\in\hat{V}=H^1_{0, \partial\Gamma}(\Gamma)$, $p\in Q$ such that
%
\begin{equation}\label{eq:coupled_weak}
  \begin{aligned}
    &\int_{\Omega}\nabla u\cdot \nabla v &\phantom{+\int_{\Gamma}\nabla \hat{u}\cdot \nabla \hat{v}} &+\int{\Gamma}p v &= \int_{\Omega}f v \quad &\forall v\in V,\\
    &\phantom{\int_{\Omega}\nabla u\cdot \nabla v} &+{\int_{\Gamma}\nabla \hat{u}\cdot \nabla \hat{v}} &-\int{\Gamma}p\hat{v} &= \int_{\Gamma}\hat{f}\hat{v} \quad &\forall \hat{v}\in \hat{V},\\
    &\int_{\Gamma}u q &-\int_{\Gamma}\hat{u}q &\phantom{-\int{\Gamma}q\hat{v}} &= \int_{\Gamma}h q \quad &\forall q\in Q.
  \end{aligned}
\end{equation}
%
\begin{figure}[h]
  \begin{center}
    \begin{tikzpicture}[scale=0.60]
      % Minus
  \draw[black, very thick] (1,0) rectangle (4, 3);
  \draw[black, very thick] (1,0) -- (4, 3);
  \node[fill=white, opacity=0.9] at (2.5, 1.5) {$\Omega^{-}_{H}$};

@@

  \draw[black, very thick] (4.5,0) -- (4.5, 3);
  \node[opacity=0.9, below] at (4.5, 0) {$\Gamma_{h}$};

  \node[mark size=3pt, color=black] at (4.5, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (4.5, 3) {\pgfuseplotmark{*}};
  % Right
    \draw[black, very thick] (5,0) rectangle (8, 3);
  \draw[black, very thick] (5,0) -- (8, 3);
  \node[fill=white, opacity=0.9] at (6.5, 1.5) {$\Omega^{+}_{H}$};

  \node[mark size=3pt, color=black] at (5, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (8, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (5, 3) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (8, 3) {\pgfuseplotmark{*}};
\end{tikzpicture}
    %
    \hspace{10pt}
    \begin{tikzpicture}[scale=0.60]
      % Minus
  \draw[black, very thick] (1,0) rectangle (4, 3);
  \draw[black, very thick] (1,0) -- (4, 3);
  \node[fill=white, opacity=0.9] at (2.75, 1.5) {$\Omega^{-}_{H}$};

@@

  \draw[black, thin, dotted] (4, 0) -- (4.5, 0);
  \draw[black, thin, dotted] (4, 3) -- (4.5, 3);
  % Center
  \draw[black, thin, dotted] (4.5, 0) -- (5, 0);
  \draw[black, thin, dotted] (4.5, 3) -- (5, 3);
     % Center
  \draw[black, very thick] (4.5,0) -- (4.5, 3);
  \node[opacity=0.9, below] at (4.5, 0) {$\Gamma_{h}$};

  \node[mark size=3pt, color=black] at (4.5, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (4.5, 1) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (4.5, 2) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (4.5, 3) {\pgfuseplotmark{*}};
  % Right
    \draw[black, very thick] (5,0) rectangle (8, 3);
  \draw[black, very thick] (5,0) -- (8, 3);
  \node[fill=white, opacity=0.9] at (6.5, 1.5) {$\Omega^{+}_{H}$};

  \node[mark size=3pt, color=black] at (5, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (8, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (5, 3) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (8, 3) {\pgfuseplotmark{*}};
    \end{tikzpicture}
        %
    \hspace{10pt}
    \begin{tikzpicture}[scale=0.60]
      % Minus
  \draw[black, very thick] (0,0) rectangle (3, 3);
  \draw[black, very thick] (0,0) -- (3, 3);
  \node[fill=white, opacity=0.9] at (2.25, 1.5) {$\Omega^{-}_{H}$};

@@

     % Center
  \draw[black, very thick] (4.5,0) -- (4.5, 3);
  \node[opacity=0.9, below] at (4.5, 0) {$\Gamma_{h}$};

@@

  \draw[black, very thick] (3,0) -- (6, 0);
  \draw[black, very thick] (3,0) -- (6, 3);
  \draw[black, very thick] (3,3) -- (6, 3);  
  % Right
    \draw[black, very thick] (6,0) rectangle (9, 3);
  \draw[black, very thick] (6,0) -- (9, 3);
  \node[fill=white, opacity=0.9] at (6.75, 1.5) {$\Omega^{+}_{H}$};

  \node[mark size=3pt, color=black] at (6, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (9, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (6, 3) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (9, 3) {\pgfuseplotmark{*}};
\end{tikzpicture}
%
\end{center}
  \caption{Different mesh settings considered for the coupled problem
    \eqref{eq:coupled_weak}: conforming matching, conforming non-matching,
    non-conforming (from left to right).
  }
\label{fig:multi_domains}
\end{figure}
%
In the following $\Omega=(0, 1)$, $\Gamma=\left\{(x, y)\in\Omega; x=\tfrac{1}{2}\right\}$
and based on the properties of the finite element meshes $\Omega_H$, $\Gamma_h$
we shall distinguish three different settings, cf. Figure \ref{fig:multi_domains}.
Here, a conforming case implies that the trace mesh of $\Omega_H$ on $\Gamma$
consists only of the existing facets of the mesh. In the conforming setting 
we consider matching and non-matching cases as defined above. We remark
that the approximation of the space $\hat{V}$ shall always be constructed
on the multiplier mesh $\Gamma_h$.

\subsection{P1-P1-P1 discretization with $\Gamma$ conformity}
Let us first consider a conforming setting and an approximation of all
the spaces involved in \eqref{eq:coupled_weak} in terms of P1 elements.
As with the Babu{\v s}ka problem \eqref{eq:bab} the discrete multiplier
space is such that $q=0$ on $\partial\Gamma$ for all $q\in Q_h$. In fact,
the boundary conditions are necessary to obtain an invertible linear system.
